\documentclass[11pt]{article}

\input{commands}
\syllabuslayout{COS~284}{Introduction to Computer Systems}{Summer}

\usepackage[colorlinks=true,allcolors=blue]{hyperref}
\usepackage{booktabs}
\usepackage{comment}

\newcommand{\submit}{\textsc{Submit}}

\begin{document}

\section{Addendum: Independent Study}

This document is an addendum
to the full COS284 syllabus
for students enrolled
in the independent study
version of the course.

\section{Instruction}
\label{sec:instruction}

Because this course is offered as independent study,
there is no regularly scheduled instruction
(e.g., lectures, recitations, labs).
You are responsible to stay up to date with the course schedule,
do required readings,
and complete and submit all assignments on time.

You are \emph{strongly} encouraged to contact the instructor at any time
with questions, comments, suggestions, or concerns.
Because this is an independent study course
with no regular meeting times,
the instructor may not be available for face-to-face meetings
at various times during the course.
However, you are always welcome to contact the instructor
by electronic mail, on-line chat (e.g., Slack),
or other means as arranged.
The instructor will make a best effort to reply to questions and concerns
in a timely manner.
If the instructor fails to reply in a reasonable time period,
he or she will make reasonable adjustments
to deliverables or due dates
as appropriate.

\section{Schedule}
\label{sec:schedule}

The course schedule presents
due dates for all course deliverables.
Refer to that document for specifics.

In any course, it is important to complete assignments on time.
This is particularly true in the case of an independent study course,
in which you are largely responsible for staying on schedule
with the course.

\section{Activities and Deliverables}

The activities and deliverables that comprise this course
are as follows.
Deliverables that you must submit to the instructor
are marked ``\submit.''

\subsection{Reading Summaries}

You are expected to read extensively in the course textbook
throughout the course.
For each reading selection, you should:
\begin{enumerate}
\item
  Read the selection carefully, completely, and for understanding.
\item
  Ask the instructor for clarification of anything you find
  difficult or confusing.
\item
  \submit{} a brief written summary of the key points covered in the reading
  as you understand it.
\end{enumerate}

\subsection{Practice Problems}

To enhance your learning,
you must complete all practice problems
associated with each reading.
\begin{enumerate}
\item
  Complete the practice problems associated with the reading.
  As suggested in the textbook,
  do the problem \emph{without} referring to the answer at the end of the chapter.
  When you are satisfied that you have answered properly,
  verify your answer with the answer in the textbook.
\item
  \submit{} your answers to the practice problems.
  For each problem,
  indicate whether you answered correctly before looking up the answer.
  If you did not answer correctly\ldots
  \begin{itemize}
  \item
    \ldots and you \emph{do} understand the textbook's answer completely,
    comment on how your initial understanding was off the mark.
  \item
    \ldots and you \emph{don't} understand the textbook's answer completely,
    comment on the source of your confusion
    so the instructor can offer additional guidance.
  \end{itemize}
\end{enumerate}

\subsection{Homework Problems}

Homework assignments
demonstrate your understanding of key course concepts.
For each homework assignment, you should:
\begin{enumerate}
\item
  Start early on the assignment so that you can complete it on time.
\item
  While working on the assignment,
  ask the instructor for clarification of anything you find
  difficult or confusing.
  Starting the homework sooner gives you more time to ask questions.
\item
  \submit{} your solution to the homework assignment.
\end{enumerate}

\subsection{Lab Assignments}

Lab assignments
give you practice applying your understanding of course concepts.
\begin{enumerate}
\item
  Labs are challenging; start early.
\item
  While working on the lab,
  ask the instructor for clarification of anything you find
  difficult or confusing.
\item
  Much of your lab work can be done on any compatible Linux system.
  However, to submit your final answers to labs,
  you must compile and submit them on a CS\&E lab machine.
\item
  \submit{} your completed lab as directed in the lab write-up.
\end{enumerate}

\subsection{Exams}

Exams in this course evaluate your mastery of course material
and also provide an opportunity for learning.
\begin{enumerate}
\item
  Because there is no regular class meeting time,
  exams are all ``take home.''
\item
  Exams take time;
  start working on exams as soon as they are available to you.
\item
  While working on an exam,
  you may refer freely to the textbook
  and any other resources you yourself have prepared.
\item
  As detailed on each exam,
  you are not allowed to refer to any
  on-line resources
  while taking the exam.
  However, you are \emph{always} welcome to contact the instructor
  with questions as you complete an exam.
\item
  \submit{} your completed exam to the instructor.
\end{enumerate}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
