\documentclass[11pt]{article}

\input{commands}
\syllabuslayout{COS~436}{Parallel and Distributed Computing}{Fall}

\usepackage[colorlinks=true,allcolors=blue]{hyperref}
\usepackage{booktabs}
\usepackage{comment}

\begin{document}

\titleblock{COS 436}{Parallel \& Distributed Computing}

\logistics{Three}{Euler Science 200}{MWF 2:00-3:00}{T/01-Dec, 1:00-3:00}

\section{Instructor}

\input{tom-details}

\begin{catalogentry}{COS~265}
  A study of concepts and models of distributed and parallel computing,
  including concurrency, synchronization, algorithms, hardware organization,
  and common programming environments.
  Implementation of parallel algorithms on multi-core CPUs and many-core GPUs.   
\end{catalogentry}

\section{Course Overview}

Most---if not all---of the courses
you have taken so far in computer science
have focused on algorithms and programs
for a single processor.
This approach to learning makes a great deal of sense.
It's plenty hard to write and debug programs
on a single processor;
why complicate matters with more than one?

For a variety of reasons that we'll discuss,
the world hasn't run exclusively on one-processor computers
for a long time.
Back in~2001, IBM released the first
two-core microprocessor---the Power4.
As we'll see,
since that watershed introduction,
multi-core, many-core, and massively parallel processors
have taken the world by storm.
You must understand these architectures
and be able to write and debug programs on them
in order to be competitive in the modern computing landscape.

In this course,
we will study
multi-core CPUs,
many-core GPUs,
and a variety of tools, technologies, and techniques
that will help you
design and write software
that maximizes the performance of modern computer systems.

\section{Learning Objectives}

Upon successful completion of this course, you should be able to:

\begin{enumerate}
\item Explain the history of high-performance computing
  and place modern parallel and distributed computing
  in its historical context.
\item Differentiate parallel computing
  from distributed computing.
\item Differentiate parallelism and concurrency.
\item Explain Flynn's taxonomy of parallel architectures.
\item Differentiate uniprocessor, many-core, and multi-core computer architectures.
\item Apply decomposition and design strategies
  for various parallel problems and architectures.
\item Formulate and implement efficient parallel versions of sequential algorithms.
\item Measure parallel algorithm performance.
\item Calculate parallel speedup and efficiency.
\item Employ a threaded model of parallel computation,
  including common parallel programming constructs
  like semaphores, shared memory, and monitors.
\item Build correct and performant software
  for both shared- and distributed-memory multicomputers
  using OpenMP and MPI.
\item Understand the host-device model
  for modern, general-purpose graphics processing units (GPUs).
\item Build correct and performant software for GPUs.
\item Construct hybrid parallel programs
  that execute cooperatively on both CPU and GPU cores.
\end{enumerate}

\section{Text}

\input{safari}

\section{Evaluation}

The grading breakdown
for the course
is shown in table~\ref{tab:grading}.
Refer to my \emph{Periodic Table of the Grades} for the grading scheme.
I reserve the right to award a higher grade than strictly earned;
outstanding attendance and class participation
figure prominently in such decisions.

\begin{table}[htb]
  \centering
  % BEGIN RECEIVE ORGTBL grades
  \begin{tabular}{lll}
    \toprule
    Category    &                 & Weight \\
    \midrule
    Assignments & Reading Quizzes & 20\%   \\
                & Programming     & 40\%   \\
    Exams       & Midterm         & 15\%   \\
                & Final           & 25\%   \\
    \midrule
                & Total           & 100\%  \\
    \bottomrule
  \end{tabular}
  % END RECEIVE ORGTBL grades
  \caption{Grading details}
  \label{tab:grading}
\end{table}

\begin{comment}
  #+ORGTBL: SEND grades orgtbl-to-latex :splice nil :skip 0 :booktabs t
  | Category    |                 | Weight |
  |-------------+-----------------+--------|
  | Assignments | Reading Quizzes |    20% |
  |             | Programming     |    40% |
  | Exams       | Midterm         |    15% |
  |             | Final           |    25% |
  |-------------+-----------------+--------|
  |             | Total           |   100% |
  #+TBLFM: @7$3=100*vsum(@I..II);%d%%
\end{comment}

\section{Course Expectations}

\input{expectations}

\section{Pandemic}

\input{covid}

\section{Course Management}

We use several systems to help manage the course
and for on-line communication.

\input{email}
\input{canvas}
\input{slack}

\section{Final Exam Policy}

\input{final-exams}

\section{Academic Integrity}

\input{cheating}

\section{Support Services}

\input{support-services}

\lastupdated

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:


% LocalWords:  MWF lll ORGTBL orgtbl booktabs TBLFM vsum
