\documentclass[11pt]{article}

\input{commands}
\syllabuslayout{COS~380}{Natural Language Processing}{Fall}

\usepackage[colorlinks=true,allcolors=blue]{hyperref}
\usepackage{booktabs}
\usepackage{comment}

% \usepackage{biblatex}
% \addbibresource{courses.bib}

\begin{document}

\titleblock{COS 380}{Natural Language Processing}

\logistics{Three}{Euler Science 103}{MWF 1:00--1:50}{M/09-Dec-2019, 8:00--10:00}

\section{Instructor}

\input{tom-details}

\begin{catalogentry}{COS~280}
  A study of the automation of human communication abilities,
  covering both textual and vocal aspects.
  Major topics include language parsing, understanding, representation,
  enhancement, generation, translation,
  and speaker/author recognition.
\end{catalogentry}

\section{Learning Objectives}

Upon successful completion of this course,
you will be able to:
\begin{enumerate}
\item Articulate the history, development, and topics
  commonly studied in Natural Language Processing (NLP)
\item Use and apply algorithms for text processing
\item Continue investigation into NLP
\item Demonstrate critical inquiry in NLP and computational linguistics
\item Use NLP for practical, hands-on purposes
\item Create software at a high level of sophistication
  using languages relevant to text processing.
\item Have an awareness of how Christians should apply the capabilities
  of Artificial Intelligence, especially those in NLP.
\end{enumerate}

\section{Possible Topics}
NLP is a very large field. We will cover some (but not all) of the following topics.
\begin{enumerate}
\item Regular expressions
\item Finite state automata
\item Finite state transducers
\item N-Grams
\item Part-of-speech tagging
\item Hidden Markov Models
\item Formal Grammars of English
\item Syntactic Parsing
\item Statistical Parsing
\item Features and Unification
\item Representation of Meaning
\item Computational Semantics
\item Lexical Semantics
\item Computational Lexical Semantics
\item Computational Discourse
\item Information Extraction
\item Question Answering and Summarization
\item Machine Translation
\end{enumerate}

\section{Project}

During the course,
you will build a non-trivial application
that demonstrates your understanding of Natural Language Processing.

\section{Text}

\input{safari}

\section{Evaluation}

The grading breakdown for the course
is shown in Table~\ref{tab:grading}.
Refer to my \emph{Periodic Table of the Grades}
for the grading scheme.
I reserve the right to award a higher grade than strictly earned;
outstanding attendance and class participation
figure prominently in such decisions.

\begin{table}[htb]
  \centering
  % BEGIN RECEIVE ORGTBL grades
  \begin{tabular}{lr}
    \toprule
    & Weight \\
    \midrule
    Homework      & 10\%   \\
    Programming   & 20\%   \\
    Participation & 10\%   \\
    Project       & 20\%   \\
    Midterm       & 20\%   \\
    Final         & 20\%   \\
    \midrule
    Total         & 100\%  \\
    \bottomrule
  \end{tabular}
  % END RECEIVE ORGTBL grades
  \caption{Grading details}
  \label{tab:grading}
\end{table}
\begin{comment}
#+ORGTBL: SEND grades orgtbl-to-latex :splice nil :skip 0 :booktabs t
|               | Weight |
|               |    <r> |
|---------------+--------|
| Homework      |    10% |
| Programming   |    20% |
| Participation |    10% |
| Project       |    20% |
| Midterm       |    20% |
| Final         |    20% |
|---------------+--------|
| Total         |   100% |
#+TBLFM: @11$2=100*vsum(@I..II);%d%%
\end{comment}

\section{Course Expectations}

\input{expectations}

\section{Course Management}

We use several systems to help manage the course
and for on-line communication.

\input{email}
\input{canvas}
\input{slack}

\section{Academic Integrity}

\input{cheating}

\section{Support Services}

\input{support-services}

\lastupdated

% \printbibliography{}\label{sec:references}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

% LocalWords:  automata Summarization lr
