\documentclass[11pt]{article}

\input{commands}
\syllabuslayout{COS~326}{Data Visualization}{Spring}

\usepackage[colorlinks=true,allcolors=blue]{hyperref}
\usepackage{booktabs}
\usepackage{comment}

\usepackage{biblatex}
\addbibresource{courses.bib}

\begin{document}

\titleblock{COS 326}{Data Visualization}

\logistics{Three}{Euler Science 040}{MWF 1:00--1:50}{W/12-May, 8:00--10:00}

\section{Instructor}

\input{tom-details}

\begin{catalogentry}{COS~120, COS~143; \textbf{encouraged}: MAT~311, Statistics course}
  This course introduces explanatory and exploratory data visualization,
  including principles, techniques, and tools,
  that facilitate understanding and action based on very big data sets.
  Principles from graphic design,
  visual perception,
  and cognitive science are considered.
  Students employ modern tools and languages to access, analyze, and visualize
  Internet-scale data.
\end{catalogentry}

\section{Learning Objectives}

Upon successful completion of this course,
you will be able to:
\begin{enumerate}
\item Articulate and employ standards of excellence in
  the presentation of visual information.
\item Understand key aspects of human perception of visual information.
\item Employ conventional tools for visualization (e.g., office software suites)
  to communicate data clearly and consistently.
\item Identify, extract, and clean Internet-scale data sets in preparation
  for visualization.
\item Use purpose built tools to analyze and visualize large, complex
  data sets (e.g.,
  \href{https://observablehq.com/}{Observable},
  \href{https://jupyter.org/}{Jupyter},
  \href{https://matplotlib.org/}{matplotlib},
  \href{https://ggplot2.tidyverse.org/}{ggplot2},
  \href{https://rstudio.com/products/rstudio/}{R~Studio}).
\item Write robust software in languages relevant to
  data science and data visualization (e.g.,
  \href{https://www.python.org/}{Python},
  \href{https://www.r-project.org/}{R},
  \href{https://developer.mozilla.org/en-US/docs/Web/JavaScript}{JavaScript},
  \href{https://www.typescriptlang.org/}{TypeScript})
\item Develop custom, interactive, Web-based visualizations
  that allow rich exploration of complex data using
  standard tools (e.g., \href{https://d3js.org/}{D3}).
\item Critique the clarity and efficacy of visualizations from other data scientists.
\item Work as a team to create visualizations of complex and socially relevant data.
\end{enumerate}

\section{Team Project}

During the course,
you and a partner
will create non-trivial visualizations
of real world data that:
\begin{enumerate}
\item Exercises your understanding of data visualization.
\item Showcases your ability and experience with data visualization techniques and tools
\item Clarifies the facts of a complex or controversial topic of relevance to
  contemporary society.
\end{enumerate}

\section{Texts}

Our principle text will be Wilke~\cite{wilke2019fundamentals}.

For programming exercises,
I recommend Murray~\cite{murray2017interactive} and
Janert~\cite{janert2019d3} for D3,
VanderPlas~\cite{vanderplas2016python} for Python,
and Wickham~\cite{wickham2016r} for R.

Other volumes of utility for D3 are 
Meeks~\cite{meeks2017d3}
(a title from the normally terrific Manning, this one is comprehensive but uninspiring visually)
and Heydt~\cite{heydt2015d3}
(a surprisingly clear text published by the very uneven Packt).
Our custom visualizations will use Scalable Vector Graphics (SVG);
Bellamy~\cite{bellamy2014svg} is a good overview.

Finally,
Edward Tufte is the leading expert on data visualization in the last 50~years.
His book
\emph{The Visual Display of Quantitative Information}~\cite{tufte1983visual}
is the modern classic in the field.
His other major publications
(\cite{tufte1990envisioning},
\cite{tufte1997visual}, and
\cite{tufte2006beautiful})
also warrant close inspection for instruction and inspiration.
His thin \emph{Cognitive Style of PowerPoint}~\cite{tufte2006cognitive}
is a fantastic critique of modern ``slide ware,''
\href{https://www.nytimes.com/2003/12/14/magazine/2003-the-3rd-annual-year-in-ideas-powerpoint-makes-you-dumb.html}{how it makes you dumb},
and how it helped bring down the Space Shuttle \emph{Challenger}.

\subsection{Safari}
\input{safari}

\section{Evaluation}

The grading breakdown for the course
is shown in Table~\ref{tab:grading}.
Refer to my \emph{Periodic Table of the Grades}
for the grading scheme.
I reserve the right to award a higher grade than strictly earned;
outstanding attendance and class participation
figure prominently in such decisions.

\begin{table}[htb]
  \centering
  % BEGIN RECEIVE ORGTBL grades
  \begin{tabular}{lr}
    \toprule
    & Weight \\
    \midrule
    Homework      & 10\%   \\
    Programming   & 20\%   \\
    Participation & 10\%   \\
    Project       & 20\%   \\
    Midterm       & 20\%   \\
    Final         & 20\%   \\
    \midrule
    Total         & 100\%  \\
    \bottomrule
  \end{tabular}
  % END RECEIVE ORGTBL grades
  \caption{Grading details}
  \label{tab:grading}
\end{table}
\begin{comment}
#+ORGTBL: SEND grades orgtbl-to-latex :splice nil :skip 0 :booktabs t
|               | Weight |
|               |    <r> |
|---------------+--------|
| Homework      |    10% |
| Programming   |    20% |
| Participation |    10% |
| Project       |    20% |
| Midterm       |    20% |
| Final         |    20% |
|---------------+--------|
| Total         |   100% |
#+TBLFM: @11$2=100*vsum(@I..II);%d%%
\end{comment}

\section{Course Expectations}

\input{expectations}

\section{Pandemic}

\input{covid}

\section{Course Management}

We use several systems to help manage the course
and for on-line communication.

\input{email}
\input{canvas}
\input{slack}

\section{Academic Integrity}

\input{cheating}

\section{Support Services}

\input{support-services}

\printbibliography{}

\lastupdated

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

% LocalWords:  MWF ORGTBL orgtbl booktabs TBLFM vsum matplotlib lr ggplot
% LocalWords:  Wilke Janert VanderPlas Wickham Meeks Heydt Packt
