\documentclass[11pt]{article}

% Past offerings
% https://gfx.cse.taylor.edu/courses/cos310/syllabus/
% https://canvas.cse.taylor.edu/courses/26 - Denning
% https://canvas.cse.taylor.edu/courses/62 - Geisler

\input{commands}
\syllabuslayout{COS~310}{Current Literature Survey}{Fall}

\usepackage[colorlinks=true,allcolors=blue]{hyperref}
\usepackage{booktabs}
\usepackage{comment}

\setcounter{tocdepth}{1}

\begin{document}

\titleblock{COS 310}{Current Literature Survey}

\logisticssg{One}{Euler Science 103}{R 9:30--10:30}{R/16-Dec, 8:00--10:00}

\input{tom-details}

\tableofcontents

\begin{catalogentry}{One 300-level COS course}
  A survey of classical and current literature in computer science.
  A goal of the course is to produce a concept
  for a research proposal with literature survey appropriate
  for an undergraduate research project.
  Students lead discussions on papers and topics of interest.
\end{catalogentry}

NOTES---JG

Whenever I teach the class, I go through ACM/IEEE paper archives focusing on
papers with awards and/or interesting titles from the past year and pull them
for reading.

I attempt to get a wide range of computing topics so students get a feel for
different types of research topics/papers they may pursue.

Unfortunately, the best papers are usually difficult to read because of
expected pre-existing understanding from the reader by the paper that our
students don't already posses.

The [topic] limit is primary for me to give them good feedback on the quality
of their survey and help them find materials.

I lead the discussion the first week or two and then turn it over to assigned
students for the rest of the semester.  They are responsible for guiding the
content, but I often add tidbits that they should learn about the research
process.

Things like what it takes to write the paper, cooperation with colleagues
(especially research advisor), how papers are selected for conferences,
differences in quality between top-level, mid-level, less quality conferences,
presenting a paper.

But those things aren't scheduled and often happen spontaneously in reference
to comments by students during the discussion.

I expect participation, but don't have a good rubric.  In the past, I've put a
tick mark by each students name when they add to the discussion, but that takes
away from my ability to pay attention to the discussion.

NOTES---JD

one thing that i did do that i thought was very helpful for students: I had
them read a paper I wrote, 3DFlow, and they filled out a review (from SIGGRAPH)
and acted as reviewers

then i would rebut and defend the paper

then for each of the following papers, 2 students would act as authors while
others acted as reviewers

in the past, we req’d them to attend a conference.  usually it was CCSC:MW
conference, because it was close, in the fall, and cheap.  frankly, the CCSC
conf was a terrible experience for almost every student, but no other conf
really fit the bill :disappointed:

so i ended up dropping that req

the other thing that i did differently from geisler/brandle is that I chose the
topics for students to do a lit survey over, rather than having students pick
as a pre-choice for research 1+2.  actually, i gave them a few options, but i
chose the options.  when i chose the topics (graphics), i had way more insight
into the topic, so i could critique better their survey and give good resources
(https://kesen.realtimerendering.com/ is an amazing treasure trove!)

also, by me choosing a topic, the students would focus on the process rather
than the topic

and there was almost always 1 or 2 students that would become laggards and just
run out of time, especially since we met only 1 time / wk for an hr

the RCR training is a must in my opinion, even if the students don’t go on to
research 1+2

\section{Learning Objectives}

Upon successful completion of this course,
you will be able to:
\begin{enumerate}
\item Read a research paper from a technical journal or conference and extract its main ideas.
\item Perform a literature search.
\item Name, describe, and apply the following critical thinking skills to research papers:
  \begin{enumerate}
  \item Analyzing an argument
  \item Determining the strength of an argument
  \end{enumerate}
\item Explain the role of critical thinking in research.
\end{enumerate}

\section{Activities}

\begin{enumerate}
\item
  Read papers each week and respond to them.
  You will each upload a response
  wherein you briefly summarize the paper and discuss the paper
  regarding how it was written as well as the content.
  In particular, you will be asked to analyze their arguments
  and comment on the strength of their arguments.
\item 
  Write a formal literature survey.
\item 
  Present on literature survey and include some potential research ideas stemming from the work done.
\item 
  Participate in classroom discussion of reading.
\item 
  Successfully go through RCR Training.
\end{enumerate}

\section{Responsible Conduct of Research (RCR) Training}

All students who will present or publish research outside of Taylor
must complete the Responsible Conduct of Research (RCR) training.
The training consists of online modules and an on campus discussion.
The online training is completed using the CITI modules
and the on-campus discussion will be held early in Fall term.

If a student member has never registered for the CITI program,
they will need to complete the following steps:

\begin{enumerate}
\item
  Go to \href{https://about.citiprogram.org/en/homepage/}.
\item 
  Click register in the upper right corner of CITI home page.
\item 
  Select Taylor University for ``Organizational Affiliation.''
\item 
  Enter your personal information (first and last name, email address).
\item 
  Create username, password, and security question.
\item 
  Continue answering questions regarding gender, etc.
\item
  Answer \texttt{No}
  for
  ``Are you interested in the option of receiving
  Continuing Education Unit (CEU) credit
  for completed CITI Program courses?''
\item 
  Use:
  \begin{enumerate}
  \item
    Institutional Email Address: your TU email address
  \item 
    Department: Computer Science and Engineering
  \item 
    Role in Research: Student Researcher - Undergraduate
  \end{enumerate}
\item 
  Choose:
  \begin{enumerate}
  \item
    Question 1: Responsible Conduct of Research for Engineering
  \item 
    Question 2: leave unchecked
  \item 
    Question 3: Class Project (INTRO/BASIC IRB)
  \end{enumerate}
\end{enumerate}

\section{Text}

There is no text for the course.
Papers will be distributed throughout the semester.

\section{Evaluation}

The grading breakdown for the course
is shown in Table~\ref{tab:grading}.
Refer to my \emph{Periodic Table of the Grades}
for the grading scheme.
I reserve the right to award a higher grade than strictly earned;
outstanding attendance and class participation
figure prominently in such decisions.

\begin{table}[htb]
  \centering
  \begin{tabular}{lr}
    \toprule
                        & Weight \\
    \midrule
    RCR Training        & 10\%   \\
    Reading Responses   & 30\%   \\
    Class Participation & 30\%   \\
    Literature Survey   & 15\%   \\
    Final Presentation  & 15\%   \\
    \midrule
    Total               & 100\%  \\
    \bottomrule
  \end{tabular}
  \caption{Grading details}
  \label{tab:grading}
\end{table}

\input{boilerplate}

\section{Acknowledgments}

Thanks to Jon Denning and Jonathan Geisler
for resources from past offerings of this course.

\lastupdated

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
