Rather than selecting a traditional textbook
that you are ``forced'' to purchase by the bookstore,
I encourage you to take advantage of
\href{https://www.oreilly.com/online-learning/}{\safari}
(formerly Safari Books Online).
\safari{}
is an outstanding subscription service that gives you access
to thousands of technical titles,
including many for this course.
You can also download complete books for off-line
access on your mobile devices.

For students, the cost to subscribe directly is about \$40/month.
Access is also included in the very affordable student membership in the
\href{https://www.acm.org/}{Association for Computing Machinery} (ACM).
The ACM is
(along with the \href{https://www.computer.org/}{IEEE Computer Society})
one of the two main professional societies for computer scientists.

Why use \safari{} instead of a standard textbook?
\begin{enumerate}
\item
  Rather than asking you to buy an entire textbook
  and use only \emph{portions} of it,
  we will be draw on multiple resources
  that are \emph{directly related} to the topics 
  covered throughout the semester.
\item
  Your total cost will be about \$120,
  which is less than the cost of some single textbooks.
  If you are taking other courses from me this semester,
  you only need to pay the fee once.
\item
  You should have experience learning from written
  and electronic resources, which you will do
  throughout your technical career.
  I have been a member of \safari{} for many years
  and find it to be an invaluable resource
  when I am learning a new technology
  or buffing up my understanding of a familiar one.
\item
  You will have immediate access to a rich collection
  of technical material to advance your learning in this
  or other computer science courses.
\end{enumerate}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

% LocalWords:  ACM
