\section{Support Services}

Be aware of the following \emph{excellent} support services
available to you as a Taylor student.

\subsection{Academic Assistance}

The Academic Enrichment Center (AEC), located in the Zondervan Library,
provides individualized academic skills help
(e.g. test preparation, note taking, planning, etc.).
Contact \textbf{Dr.\ Scott Gaier}, \texttt{scgaier@taylor.edu}.
 
\subsection{Tutoring}

Peer Tutoring Services,
located in the AEC in Zondervan Library,
provides free help to students in most content areas.
For further information, contact
\textbf{Darci Nurkkala}, \texttt{drnurkkala@taylor.edu}.


\subsection{Library}

The Zondervan Library helps students
identify, obtain, and evaluate
information and resources
for papers, projects, and other academic work.
Contact them for research assistance:
\begin{enumerate}
\item
  Email: \texttt{zonlib@taylor.edu}
\item
  Phone: 765/998-4357
\item
  In person at the \textbf{Ask} desk:
  \begin{enumerate}
  \item Monday--Thursday:\ noon--midnight
  \item Friday:\ noon--8pm
  \item Saturday:\ 9am--8pm
  \item Sunday:\ 3pm--midnight
  \end{enumerate}
\item By appointment for consultation, especially for larger projects, email:
  \begin{enumerate}
  \item \textbf{Lana Wilson}, \texttt{lnwilson@taylor.edu}
  \item \textbf{David Dunham}, \texttt{david\_dunham@taylor.edu}
  \end{enumerate}
\end{enumerate}

\subsection{Writing Center}

Writing Center tutors can help you on all of your writing
in any stage of your writing process,
but they will usually focus on content and organization
before they look at grammar and style.
Expect to be actively involved during your session,
whether you are developing a better thesis,
reorganizing your main points,
or consulting a style manual to understand formatting rules.
To arrange an appointment visit \url{taylor.mywconline.com}.

\subsection{Students with Special Needs}

The Academic Enrichment Center provides a variety of services
for students who have disabilities.
This includes, but is not limited to, mental, emotional, physical, and learning disabilities.
Contact \textbf{Dr.\ Scott Barrett}, \texttt{scott\_barrett@taylor.edu}, to learn more.
If you need accommodations due to a disability,
please also see me so that I can help accordingly.

\subsection{Counseling Services}

The stresses of academic life can be hard for anyone.
Too often, mental health issues get ignored until they become unmanageable.
Just as with physical well-being,
we all need to 
stay on top of our mental health as well.
Taylor has terrific counseling services available
to help you navigate these issues.
See the course web site for an up-to-date overview of available
services
and contact information.


% LocalWords:  Zondervan Gaier AEC

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
